ExpressionView file format

### 2010-05-05 RExpressionView/inst/doc/ExpressionView.format.Rnw
EV file format vignette: use 'listings' instead of 'fancyvrb', better results.

% \VignetteIndexEntry{ExpressionView file format}
\documentclass{article}
\usepackage{ragged2e}
\usepackage{url}
\usepackage{fancyvrb}
\usepackage{color}

@@

\DefineVerbatimEnvironment%
    {XML}{Verbatim}{fontsize=\small,frame=single,rulecolor=\color{green}}

\DefineVerbatimEnvironment%
    {schema}{Verbatim}{fontsize=\small,frame=single,rulecolor=\color{blue}}

@@

\setlength{\parindent}{12pt}

@@

The EVF data file, used by ExpressionView, is a standard XML file. The
R package contains an XML Schema file that describes the exact
format. In the following we will show this schema file and explain its
parts step by step, while also showing samples from an example EVF
data file. Parts of the schema file appear in blue boxes, EVF file
code snipplets are in boxes with green frames.

@@

Finally, the expression data in included in the \texttt{<data>}
tag. This is a Base64 encoded string, generated by representing each
expression value with a single unsigned byte, and then concatenating
and Base64 encoding these bytes. This data looks like this:
\begin{XML}
<data>
/Acs1hZT+FDeFGH/29zL+3rK4+sTCvzZzxVgvNrM5Bw8Kfjw2vb6Of8qti943/0QIF8xJy7g
zMoOqyYA4/ne1KsZ1bH69u3c28zewtQM9G8T5zGK7P0szwIM/ub2z9zwHxclIdz3ywC6xtfO
DewMklghAfGqzsQtDeHZ3wolAC1GSN+9N+/i5Oz99bTzzRb1QvzHE+Qlr1Ej1U697+AFvtyn
...
</data>
\end{XML}

>>>>

% \VignetteIndexEntry{ExpressionView file format}
\documentclass{article}
\usepackage{ragged2e}
\usepackage{url}
\usepackage{listings}
\usepackage{color}
\usepackage{courier}

@@

\definecolor{green}{rgb}{0.8,1,0.8}
\definecolor{blue}{rgb}{0.8,0.8,1}
\lstset{basicstyle=\footnotesize\ttfamily,%
        keywordstyle=\footnotesize\ttfamily,%
        language=XML,frame=single,columns=fullflexible}
\lstnewenvironment{schema}{\lstset{backgroundcolor=\color{green}}}{}
\lstnewenvironment{XML}{\lstset{backgroundcolor=\color{blue}}}{}

@@

\setlength{\parskip}{12pt}

@@

The EVF data file, used by ExpressionView, is a standard XML file. The
R package contains an XML Schema file that describes the exact
format. In the following we will show this schema file and explain its
parts step by step, while also showing samples from an example EVF
data file. Parts of the schema file appear in green boxes, EVF file
code snipplets are in blue boxes.

@@

Finally, the expression data in included in the \texttt{<data>}
tag. This is a Base64 encoded string, generated by representing each
expression value with a single unsigned byte, and then concatenating
and Base64 encoding these bytes. This data looks like this:
\begin{XML}
<data>
/Acs1hZT+FDeFGH/29zL+3rK4+sTCvzZzxVgvNrM5Bw8Kfjw2vb6Of8qti943/0QIF8xJy7g2ufB
zMoOqyYA4/ne1KsZ1bH69u3c28zewtQM9G8T5zGK7P0szwIM/ub2z9zwHxclIdz3ywC6xtfOySje
DewMklghAfGqzsQtDeHZ3wolAC1GSN+9N+/i5Oz99bTzzRb1QvzHE+Qlr1Ej1U697+AFvtynDeHd
...
</data>
\end{XML}
